JCR-14-0358​ entitled ``Enemy at the Gates: Variation in Economic Growth from Civil Conflict''

### 2015-08-20 LaTeX/Revision/rev1.tex
gdp gr versus mindist

\begin{itemize}
\item \textcolor{blue}{\emph{
	We reran the models per this specification and have included the results in the appendix. In both low intensity and high intensity cases we find that the distance variables remain significant and in the hypothesized direction. 
}}
\end{itemize}

>>>>

\begin{itemize}
\item \textcolor{blue}{\emph{
	We reran the models per this specification and have included the results in the appendix. In both low intensity and high intensity cases we find that the distance variables remain significant and in the hypothesized direction, but as R1 expected the $\beta$ estimate of our distance variables was noticeably higher when using high intensity versus low intensity civil conflict cases. 
}}
\end{itemize}
